---
title: "Functional diversity patterns of fish, corals and algae in the Brazilian biogeographic province"
output: github_document
---



<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
<!-- badges: end -->



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Repository containing the data and scripts used in the article "Functional diversity patterns of fish, corals and algae in the Brazilian biogeographic province", accepted in Journal of Biogeography (February 2023).

Occurrence data (folder "data/detection") are formatted according to the Darwin Core Standards (https://www.tdwg.org/standards/dwc/). Trait data follow the basic format of trait datasets: species in the rows and traits in the columns.

The dataset of coral traits (compiled by Jessica Bleuel, PhD candidate in the Universidade Federal do Rio Grande do Norte, supervised by Dr. Guilherme O. Longo) has an embargo to be released (up to February 2024).

Zenodo's link: [![DOI](https://zenodo.org/badge/289125423.svg)](https://zenodo.org/badge/latestdoi/289125423)


<!-- badges: start -->
<!-- badges: end -->


#### This paper was produced using the following software and associated packages:

```{r pressure, echo=F,warning=F,message=F}

source("R/packages.R")
sessionInfo()


```

